Wellcome Open Research Article Template

### 2023-02-07 manuscript/manuscript.tex
add citations

For two-week-ahead-forecasts of incident cases, the Forecast Hub ensemble outperformed all crowd forecasting ensembles as measured by the weighted interval score (WIS), with the direct crowd forecasts performing poorest (see Figure \ref{fig:performance} and Table \ref{tab:scores}). When looking at WIS values after applying a log-transformation, all crowd forecasting approaches outperform the Forecast Hub ensemble. Similarly to what was observed previously \citep{bosseComparingHumanModelbased2022, KATH} do all forecasts for cases exhibit underdispersion, i.e. forecasts on average are too narrow and not uncertain enough, with empirical coverage below nominal coverage for all models.

@@

{\small\bibliographystyle{unsrtnat}
\bibliography{sample}}

\bigskip
References can be listed in any standard referencing style that uses a numbering system
(i.e. not Harvard referencing style), and should be consistent between references within
a given article.

Reference management systems such as Zotero provide options for exporting bibliographies as Bib\TeX{} files. Bib\TeX{} is a bibliographic tool that is used with \LaTeX{} to help organize the user's references and create a bibliography. This template contains an example of such a file, \texttt{sample.bib}, which can be replaced with your own. Use the \verb|\cite| command  to create in-text citations, like this \cite{Smith:2012qr} and this \cite{Smith:2013jd}.

>>>>

For two-week-ahead-forecasts of incident cases, the Forecast Hub ensemble outperformed all crowd forecasting ensembles as measured by the weighted interval score (WIS), with the direct crowd forecasts performing poorest (see Figure \ref{fig:performance} and Table \ref{tab:scores}). When looking at WIS values after applying a log-transformation, all crowd forecasting approaches outperform the Forecast Hub ensemble. Similarly to what was observed previously \citep{bosseComparingHumanModelbased2022, sherrattPredictivePerformanceMultimodel2022a} do all forecasts for cases exhibit underdispersion, i.e. forecasts on average are too narrow and not uncertain enough, with empirical coverage below nominal coverage for all models.

@@

{\small\bibliographystyle{unsrtnat}
\bibliography{software, uk-forecasting-challenge}}

\bigskip
